---
title: "Poorman_Test : Miguel Gutierrez"
output: html_notebook
---

# Point 1

1) Add new columns to the following dataset which equate to the mean, median and the sum of each row. 

```{r}
df <- data.frame(x = runif(6), y = runif(6), z = runif(6))
df$Mean = apply(df[,c('x','y','z')],1,function(x) mean(x))
df$Median = apply(df[,c('x','y','z')],1,function(x) median(x))
df$Sum = apply(df[,c('x','y','z')],1,function(x) sum(x))
df
```
# Point 2


2) Using `stats::reshape()`, change the following dataset to wide format such that there is one row per sample and then reshape it back to the original shape.


```{r}
df <- data.frame(sample = c(rep(1, 10), rep(2, 10)), test = rep(1:10, 2), values = runif(20))
df
```

we change the format such that there is one row per sample

```{r}
reshaped = reshape(df, v.names = "values", idvar = "sample",timevar = "test", direction = "wide")
reshaped
```

Now we are reshaping it back


```{r}
original = reshape(reshaped, direction = "long")
original = original[order(original$sample),]
original
```
# Point 3

3) Using `stats::reshape()`, reshape the following data to long format such that there are five columns: `sex`, `age`, `id`, `exam` and `score`. Then reshape the data back into the original format.

```{r}
df <- structure(list(
  sex = c(1L, 1L, 0L, 0L, 1L, 1L, 0L, 1L, 0L, 1L),
  age = rep(c(15L, 16L), 5),
  exam1 = c(34L, 47L, 41L, 44L, 47L, 42L, 57L, 61L, 53L, 42L),
  exam2 = c(46L, 54L, 47L, 41L, 65L, 41L, 62L, 59L, 61L, 39L),
  exam3 = c(45L, 49L, 40L, 40L, 60L, 57L, 63L, 49L, 61L, 42L),
  exam4 = c(39L, 53L, 39L, 50L, 50L, 72L, 55L, 44L, 57L, 42L),
  exam5 = c(36L, 61L, 51L, 26L, 56L, 31L, 41L, 66L, 56L, 41L)
), class = "data.frame", row.names = c(NA, -10L))
df
```

First we reshape in long  format


```{r}
reshaped = reshape(df, sep ="",varying = 3:7, direction = "long")
reshaped = reshaped[order(reshaped$sex,reshaped$age),]
names(reshaped)[names(reshaped)=="exam"] = "score"
names(reshaped)[names(reshaped)=="time"] = "exam"
reshaped
```

then again in original format

```{r}
reshape(reshaped, v.names = "score",timevar = "exam",direction = "wide")
```

# Point 4


4) Using `stats::reshape()`, reshape the following data to a wide format with the resulting columns: `id`, `min.1`, `max.1`, `min.2`, `max.2.` Then reshape the data back to the original shape.

```{r}
df <- data.frame(id = rep(1:4, each = 2), sample = rep(c(1, 2), 4), min = 1:8, max = 3:10)
df
```
First we reshape the data as proposed in the testa


```{r}
reshaped = reshape(df, v.names = c("min","max"), idvar = "id",timevar = "sample", direction = "wide")
reshaped
```

Now we reshaped the data back to the original shape

```{r}
original = reshape(reshaped, varying=2:5, direction = "long")
names(original)[names(original)=="time"] = "sample"
original
```


